Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-19 paper/paper.tex
added 3 figs+captions

\title{Region-network sparsity priors for\\
high-dimensional inference in fMRI data}

@@

\author{Danilo Bzdok, Karl Zilles, Michael Eickenberg,
  Ga\"el Varoquaux, Bertrand Thirion\\
  Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
  INRIA, Parietal team, Saclay, France\\
  CEA, Neurospin, Gif-sur-Yvette, France\\
  firstname.lastname@inria.fr}

@@

\textbf{\\keywords}:
Brain Imaging, Functional Specialization, Functional Integration,
Sparsity-inducing Norms, Structured Sparsity,
Numerical Optimization, Systems Neuroscience

@@

\begin{comment}

@@

\section{Experimental Results}
\paragraph{Serial versus parallel structure discovery and classification.}

@@

\paragraph{Acknowledgment}
{\small The research leading to these results has received funding from the
European Union Seventh Framework Programme (FP7/2007-2013)
under grant agreement no. 604102 (Human Brain Project).
Data were provided by the Human Connectome Project.
Further support was received from
the German National Academic Foundation (D.B.)
and the MetaMRI associated team (B.T., G.V.).
}

\end{comment}

>>>>

\title{Region-network hierarchical sparsity priors for\\
high-dimensional inference in brain imaging}

@@

\author{Danilo Bzdok, Michael Eickenberg,
  Ga\"el Varoquaux, Bertrand Thirion\\
  Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
  INRIA, Parietal team, Saclay, France\\
  CEA, Neurospin, Gif-sur-Yvette, France\\
  firstname.lastname@inria.fr}

@@

\textbf{\\keywords}:
Sparsity-inducing Norms, Structured Sparsity, Numerical Optimization,
Systems Neuroscience, Brain Imaging,
Functional Specialization, Functional Integration

@@

@@

\section{Experimental Results}
\paragraph{Serial versus parallel structure discovery and classification.}
\paragraph{Serial versus parallel structure discovery and classification.}
\paragraph{Serial versus parallel structure discovery and classification.}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/reg_net_prior.pdf}
\end{centering}
\vspace{-0.5cm}
\caption{\textbf{Building blocks of the region-network tree.}
Depicts neurobiological priors introduced into supervised estimation
by means of hierarchical structured sparsity.
\textit{Left:} Continuous, partially overlapping brain network priors
(\textit{hot-colored}, taken from \cite{smith2009})
accommodate the functional integration
perspective of functional brain organization.
\textit{Right:} Discrete, non-overlapping brain region priors
(\textit{single-colored}, taken from \cite{crad12})
accommodate the functional segregation perspective.
\textit{Middle:} These predefined voxel groups are incorporated
into hierarchical priors of brain networks with their
assigned brain regions.
\textit{Top to bottom:} Four examplary region-network priors
are shown.
They include the early cortex that processes
visual and sound information from the environment,
a well-known attentional circuit in the left brain hemisphere,
and
the cerebellum that realizes motor behavior.
}
\label{fig_priors}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/dataratio.pdf}
\end{centering}
\vspace{-0.5cm}
\caption{\textbf{Ordinary versus structured sparse model estimation
as a function of training set size.}
Ordinary $ell_1$-penalized logistic regression
(\textit{upper row})
is compared
to logistic regression estimation structured
by hierarchical tree prior
(\textit{lower row})
with increasing fraction (\textit{columns})
of the available training data.
Unthresholded coronal maps of model weights are
shown for comparison against
the class-wise mean neural activty
in the \textit{rightmost column}.
The 18-class out-of-sample performance in percent.
%
In the data-scarce scenario,
typical for common brain imaging studies,
hierarchical tree sparsity achieves
better support recovery with the biggest difference
in model performance comparing to
$ell_1$-penalized logistic regression.
%
In the data-riche scenario,
neurobiologically informed logistic regression
profits more from the increased information quantities than
neurobiologically naive logistic regression.
}
\label{fig_dataratio}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
\end{centering}
\vspace{-0.5cm}
\caption{\textbf{Support recovery as a function of
region and network emphasis.}
The relative impact of the region and network priors
on model selection
is systematically varied against each other.
This region-network ratio (\textit{upper row}) weighted voxel groups
to priviledge sparse models in function space
that acknowledge known data neighborhoods underlying brain region
(\textit{left columns}) or
known compartments in the data that correspond to brain networks
(\textit{right columns}).
Among the 18 classes, the model weights are shown for the
tasks (\textit{from top to bottom}) tongue movement, listening stories,
taking somebody else's perspective (ToM, "theory of mind"),
as well as
perceiving locations and tools.
The 18-class out-of-sample performance is indicated
on the \textit{bottom} and
the class-wise mean neural activty
in the \textit{rightmost column}.
%
Different emphasis on regions versus networks
in hierarchical structured sparsity can
yield essentially similar model performance.
%
Priviledging region versus network structure during model selection
recovers complementary aspects of the brain activity pattern.
%
Equal region and network emphasis yields more dispersed,
less interpretable predictive model choices.
}
\label{fig_ratio}
\end{figure}

DATARATIO

tell #maps per percent

@@

\paragraph{Acknowledgment}
{\small The research leading to these results has received funding from the
European Union Seventh Framework Programme (FP7/2007-2013)
under grant agreement no. 604102 (Human Brain Project).
Data were provided by the Human Connectome Project.
Further support was received from
the German National Academic Foundation (D.B.),
the German Research Foundation (BZ2/2-1 and BZ2/3-1 to D.B.),
and the MetaMRI associated team (B.T., G.V.).
}
